### 2015-06-05 chapters/use_cases.tex
wraps line at character width 80 in all tex files

@@

\section{({[}ː\textbar{}ʰ\textbar{}ʼ\textbar{}ʿ\textbar{}ʾ\textbar{}̜\textbar{}̠\textbar{}̟\textbar{}͡\textbar{}̪\textbar{}̰\textbar{}̣\textbar{}̥\textbar{}̩\textbar{}‿\textbar{}.\textbar{}→\textbar{}˻\textbar{}+\textbar{}̃\textbar{}̫\textbar{}̤{]})}\label{ux2d0ux2b0ux2bcux2bfux2be.}

>>>>

\section{Cross-orthographic analysis of writing systems}

Given that orthography profiles are stored in a standard CSV format, we can use
tools for converting and working with CSV. One such tool is the command line
utility \textsc{csvkit}.\footnote{\url{https://csvkit.readthedocs.org}}

% insert some examples of creating a table of language | grapheme, language |
orthographic contexts % any measure of writing systems complexity?

@@

\section{({[}ː\textbar{}ʰ\textbar{}ʼ\textbar{}ʿ\textbar{}ʾ\textbar{}̜\textbar{}̠\textbar{}̟\textbar{}͡\textbar{}̪\textbar{}̰\textbar{}̣\textbar{}̥\textbar{}̩\textbar{}‿\textbar{}.\textbar{}→\textbar{}\textbar{}+\textbar{}̃\textbar{}̫\textbar{}̤{]})}\label{ux2d0ux2b0ux2bcux2bfux2be.}
